Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-02 Draft/draft.tex
Honghao: edits up to section 6.2

%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,cgsv2017} and device independent quantum cryptography
\cite{qkd2011,qkd2014,miller2016,fu2018,eat2018}.

@@

Before giving the representations, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	\label{eq:w_subspace}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.

@@

\textbf{The linear system game}.
Recall that the the linear system game with solution group $\Gamma_r$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
equations labelled by $i \in \{1, 2 \dots \mr\}$.
We denote the associated linear system by $H\underline{x} = \uc$ and
define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$ and $I_i = \{ k : H(i,k) = 1\}$.
From the construction of $\Gamma_r$, we know that $| I_i| \leq 3$.
The correspondence between $\ux$ and the generators of $\Gamma$ is that
\begin{align*}
	&\ux(j) := a_j &&&&\text{ for } j = 1 \dots r+5 \\
	&\ux(r+6+j) := f_j&& \ux(r+9+j) := g_j &&\text{ for } j = 0,1,2 
\end{align*} 
The correspondence can be arbitrary for $j > r+11$.
We conduct the linear constraint test in a way such that Bob is always get a variable label
but Alice gets either an equation label, in which case she needs to give the full assignment to this equation,
or a pair of equation label and variable label, in which case she only needs to give the assignment to the particular 
variable in the given equation. In this way, we force Alice and Bob to use an binary observable strategy for the linear constraint 
test.

\textbf{The extended weighted CHSH test}.
In this test, 
the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
For each question, there is an associated answer set:
\begin{itemize}
	\item when the question is $\ast$, the answer set is $\{\diamond, \perp\}$;
	\item when the question is $1$ or $2$, the answer set is $\{0,1\}$;
	\item when the question is $\nr+1$ or $\nr+2$, the answer set is $\{0, 1, \perp\}$.
\end{itemize}
Note that when the referee wants to ask Alice $x = 1,2$, the referee gives Alice a pair $(i_x. x)$ where 
$i_x$ labels an equation containing the variable labelled by $x$. 
For simplicity we omit the $i_x$ part in the alphabet $\calX$.
Later we will show that the $i_x$ part can be made implicit.
The test is conducted in the following way:
\begin{enumerate}
	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{\diamond, \perp\}$;
	\item if $x = y \in \{1,2\}$, Alice and Bob should answer with $a = b \in \{0, 1\}$, as in the linear constraint test;
	\item if $x = y \in \{n+1, n+2\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
	\item if $x \in \{1,2\}$ and $y \in \{n+1, n+2\}$, 
		\begin{enumerate}
		\item if they answer with $a,b \in \{0,1\}$, then
	they should maximize $\ip{\I_{\cot(-\pi/d)}}$ with Alice and Bob's roles flipped, 
		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
		\end{enumerate}
	\item if $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$,
	\begin{enumerate} 
		\item if they answer with $a,b \in \{0,1\}$, then
		they should maximize $\ip{\I_{\cot(-\pi/d)}}$, 
		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
	\end{enumerate}
	\item $x \in \{n+1,n+2\}, y = \ast$ 
		\begin{enumerate}
		\item if Bob answers with $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$, 
		\item if Bob answers with $\perp$ Alice should answer with $\perp$ too;
		\end{enumerate}
	\item $x = \ast, y \in \{n+1, n+2\}$
	\begin{enumerate}
		\item if Alice answers with $\diamond$, Bob should answer with $\{0.1\}$ but not $\perp$, 
		\item if Alice answers $\perp$, Bob should answer $\perp$ too.
	\end{enumerate}
\end{enumerate}

\textbf{The commutation test.}
In this test, we reuse questions from the two other tests so the answer
set for each question is the same across the tests.
There are $8$ test cases.
In each test case, Alice is given one of two questions.
One of the possible question is to assign a value to some variable of the linear constraint test.
Again, the equation label is implicit when this variable is given.
The other possibility is to answer $\nr+1$ or $\nr+2$.
Bob is given both of the question so he needs to give answers to both questions.
Their answers should agree on the question that is given to both.
The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
Alice's input is determined by the pair so she receives one of the two questions with equal probability.

The full correlation is generated by a strategy that can pass all the three tests. We give the ideal strategy first.
%--------------------------------------------
\subsection{The ideal strategy}
%--------------------------------------------
Recall the two subspaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
In the ideal strategy Alice and Bob share the state 
\begin{align*}
\ket{\psi} = &(\frac{1}{\sqrt{2}} \ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
=&(\frac{1}{\sqrt{2}} \ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
\end{align*}
Here we introduce the second basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
the observables used in the extended weighted CHSH test have a simpler form.
The two basis are related by
\begin{align*}
	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) && \text{for } j = 1 \dots \frac{d-1}{2}.
\end{align*}
We define two subspaces $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$ on
$W_{d-1}$ and
define $\Pi_V$ and $\Pi_{V^\perp}$ to be the corresponding projectors. Note that $V$ is the subspace on which they should maximize $\ip{\I_{\cot(-\pi/d)}}$.
We define the states for the measurements used in the extended weighted CHSH test as follows
\begin{align*}
	&\ket{1_1} = \cos(-\pi/2d)\ket{1} + \sin(-\pi/2d)\ket{d-1}
	&&\ket{(d-1)_1} = \sin(-\pi/2d)\ket{1} - \cos(-\pi/2d)\ket{d-1}\\
	&\ket{1_2} = \cos(-\pi/2d)\ket{1} - \sin(-\pi/2d)\ket{d-1}
	&&\ket{(d-1)_2} = \sin(-\pi/2d)\ket{1} + \cos(-\pi/2d)\ket{d-1}\\
	&\ket{+} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
	&&\ket{-} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
\end{align*}
Then the measurements are
\begin{align*}
	&M_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && M_\ast^\perp = M_{n+1}^\perp = M_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&N_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && N_\ast^\perp = N_{n+1}^\perp = N_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{+}{+} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{-}{-}\\
	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_1}{1_1} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_1}{(d-1)_1}\\
	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_2}{1_2} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_2}{(d-1)_2}.
\end{align*}
To present the observables used in the linear constraints test, we relabel the generators of $\Gamma$ as $x_i$ for $i = 1 \dots \nr$. Then the 
observables are
\begin{align}
	M_i = N_i = \Psi(x_i),
\end{align}
where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
To make sure the strategy is correct, there are some facts to check.
\begin{proposition}
Let $M_1 = N_1 :=\Psi(a_1)$, $M_2 = N_2 := \Psi(a_2)$, $M_3 = N_3 := \Psi(a_3)$
and $M_4 = N_4 := \Psi(a_4)$, then
\begin{align}
	\label{eq:mn_preserve} &M_i N_i \ket{\psi} = \ket{\psi} && \text{for } i = 1 \dots 4,\\
	\label{eq:o2_comm} &(M_3M_4)M_2(M_4M_3) = M_2,
\end{align}
and similar commutation relation holds on Bob's side too.
\end{proposition}
\begin{proof}
	Since all the operators involved in this proposition act trivially on $W_2^{\x 2}$, we focus on
	their actions on $W_{d-1}$. In the later proof, by $\ket{\psi}$ we mean the part of $\ket{\psi}$ on $W_{d-1}$.

	We prove \cref{eq:o2_comm} first. It is simple to check that
	\begin{align}
		&M_1M_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},\\
		&M_3M_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
	\end{align}
	and that 
	\begin{align}
		M_3M_4 M_2 M_4 M_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = M_2.
	\end{align}

>>>>

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,cgsv2017} and device independent quantum cryptography
\cite{qkd2011,qkd2014,miller2016,fu2018,eat2018}.

@@

Before giving the representations, we define two Hilbert spaces $W_{d-1}$ and $W_2$, which will form the carrier spaces
of the representations,
\begin{align}
	\label{eq:w_subspace}
	W_{d-1} := \spn(\{\ket{x_j}\}_{j=1}^{d-1}) && W_2 = \spn(\ket{x_1}, \ket{x_2}).
\end{align}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, where the subscript $r^j$ is taken
modulo $d$ implicitly. We use the second form of the basis when it is convenient.
We denote the identity operator for these two spaces by $\1_{W_{d-1}}$ and $\1_{W_2}$.
On the Hilbert space $W_2$, we define
\begin{align*}
	X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1} &&
	Y_{W_2} = i\ketbra{x_1}{x_2} - i \ketbra{x_2}{x_1} &&
	Z_{W_2} = \ketbra{x_1}{x_1} - \ketbra{x_2}{x_2},
\end{align*}
\begin{definition}
The representation, $\Psi_0$, of $G_0$ on $W_{d-1}$ is defined by
\begin{align*}
	\Psi_0(a_1) =&\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} \\
	\Psi_0(a_2) = &\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}}\\
	\Psi_0(a_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	\Psi_0(a_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right),
\end{align*}
where $\{ \ket{u_j} \}_{j=0}^{d-2}$ is a another basis of $W_{d-1}$ given by
\begin{align*}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align*}
The representation of the rest of the generators
can be constructed from $\Psi_0(a_1)$, $\Psi_0(a_2)$, $\Psi_0(a_3)$ and $\Psi_0(a_4)$ following the 
conjugation relations.
\end{definition}
We can check that
\begin{align*}
	\Psi_0(a_1a_2) =  \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}} &&
	\Psi_0(a_3a_4) =  \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
\end{align*}
which satisfy the relation $\Psi_0(a_3a_4) \Psi_0(a_1a_2) \Psi_0(a_4a_3) = \Psi_0(a_1a_2)^r$ and
$[\Psi_0(a_3a_4), \Psi_0(a_2)] = \1_{W_{d-1}}$.

@@

Recall that the the linear system game with solution group $\Gamma_r$ defined in \cref{def:gamma} has variables labelled by $j \in \{1,2,\dots,\nr\}$ and
equations labelled by $i \in \{1, 2 \dots \mr\}$.
We denote the associated linear system by $H\underline{x} = \uc$ and
define $X_i := \{ \ux : \sum_{k} H(i,k)\ux(k) = \uc(i) \}$ and $I_i = \{ k : H(i,k) = 1\}$.
From the construction of $\Gamma_r$, we know that $| I_i| \leq 3$.
The correspondence between $\ux$ and the generators of $\Gamma$ is that
\begin{align*}
	&\ux(j) := a_j &&&&\text{ for } j = 1 \dots r+5 \\
	&\ux(r+6+j) := f_j&& \ux(r+9+j) := g_j &&\text{ for } j = 0,1,2 
\end{align*} 
The correspondence can be arbitrary for $j > r+11$.
We conduct the linear constraint test in a way such that Bob is always get a variable label
but Alice gets either an equation label, in which case she needs to give the full assignment to this equation,
or a pair of equation label and variable label, in which case she only needs to give the assignment to the particular 
variable in the given equation. In this way, we force Alice and Bob to use an binary observable strategy for the linear constraint 
test.

In the extended weighted CHSH test,
all the question pairs are $\{ (\ast, \ast) \} \cup \{(\ast, y), (x, \ast)\}_{x,y = \nr+1, \nr+2} \cup 
\{(x,y)\}_{x=y \in \{\nr+1, \nr+2\}} \cup
\{(x,y)\}_{x = y \in \{1, 2\}} \cup \{(x,y)\}_{x = 1,2, y =\nr+1, \nr+2} \cup  \{(x,y)\}_{x = \nr+1,\nr+2, y =1, 2}$.
%the input alphabets are $\calX = \calY = \{\ast, 1, 2, \nr+1,\nr+2\}$.
For each question, there is an associated answer set:
\begin{itemize}
	\item when the question is $\ast$, the answer set is $\{\diamond, \perp\}$;
	\item when the question is $1$ or $2$, the answer set is $\{0,1\}$;
	\item when the question is $\nr+1$ or $\nr+2$, the answer set is $\{0, 1, \perp\}$.
\end{itemize}
Note that when the referee wants to ask Alice $x = 1,2$, which also labels a variable of $\LS(\Gamma_r)$, 
the referee gives Alice a pair $(i_x. x)$ where 
$i_x$ labels an equation containing the variable labelled by $x$. 
For simplicity we omit the $i_x$ part in the alphabet $\calX$, since $\LS(\Gamma_r)$
forces Alice to use a binary observable strategy.
Later we will show that the $i_x$ part can be made implicit.
The test is conducted in the following way:
\begin{enumerate}
	\item if $x = y = \ast$, Alice and Bob should answer with $a = b \in \{\diamond, \perp\}$;
	\item if $x = y \in \{1,2\}$, Alice and Bob should answer with $a = b \in \{0, 1\}$, as in the linear constraint test;
	\item if $x = y \in \{n+1, n+2\}$, Alice and Bob should answer with $a = b \in \{0, 1, \perp\}$;
	\item if $x \in \{1,2\}$ and $y \in \{n+1, n+2\}$, 
		\begin{enumerate}
		\item if they answer with $a,b \in \{0,1\}$, then
	they should maximize $\ip{\I_{\cot(-\pi/d)}}$ with Alice and Bob's roles flipped, 
		\item if Bob answers with $\perp$, then Alice's answer doesn't matter;
		\end{enumerate}
	\item if $x \in \{n+1, n+2\}$ and $y \in \{1,2\}$,
	\begin{enumerate} 
		\item if they answer with $a,b \in \{0,1\}$, then
		they should maximize $\ip{\I_{\cot(-\pi/d)}}$, 
		\item if Alice answers with $\perp$, then Bob's answer doesn't matter;
	\end{enumerate}
	\item $x \in \{n+1,n+2\}, y = \ast$ 
		\begin{enumerate}
		\item if Bob answers with $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$, 
		\item if Bob answers with $\perp$ Alice should answer with $\perp$ too;
		\end{enumerate}
	\item $x = \ast, y \in \{n+1, n+2\}$
	\begin{enumerate}
		\item if Alice answers with $\diamond$, Bob should answer with $\{0.1\}$ but not $\perp$, 
		\item if Alice answers $\perp$, Bob should answer $\perp$ too.
	\end{enumerate}
\end{enumerate}

In the commutation test, 
we reuse questions from the two other tests so the answer
set for each question is the same across the tests.
There are $8$ test cases.
In each test case, Alice is given one of two questions.
One of the possible question is to assign a value to some variable of $\LS(\Gamma_r)$.
Again, the equation label is implicit when this variable is given.
The other possibility is to answer $\nr+1$ or $\nr+2$ from the extended weighted CHSH test.
Bob is given both of the question so he needs to give answers to both questions.
Their answers should agree on the question that is given to both.
The $\calY$ has $8$ pairs, $\calY = \{ (\nr+1, j), (\nr+2, j) \}_{j = r+6, r+8, r+9, r+11}$.
Alice's input is determined by the pair so she receives one of the two questions of a given pair with equal probability.

The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first.
%--------------------------------------------
\subsection{The ideal strategy}
%--------------------------------------------
Recall the two subspaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
In the ideal strategy Alice and Bob share the state 
\begin{align*}
\ket{\psi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
=&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
\end{align*}
Here we introduce the second basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
the observables used in the extended weighted CHSH test have a simpler form.
The two basis are related by
\begin{align*}
	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) && \text{for } j = 1 \dots \frac{d-1}{2}.
\end{align*}
We define two subspaces $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$ on
$W_{d-1}$ and
define $\Pi_V$ and $\Pi_{V^\perp}$ to be the corresponding projectors. Note that $V$ is the subspace on which they should maximize $\ip{\I_{\cot(-\pi/d)}}$.
We define the states for the measurements used in the extended weighted CHSH test as follows
\begin{align*}
	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1}\\
	&\ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
\end{align*}
Then the measurements are
\begin{align*}
	&M_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && M_\ast^\perp = M_{n+1}^\perp = M_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&N_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && N_\ast^\perp = N_{n+1}^\perp = N_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}\\
	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_+}{1_+} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_+}{(d-1)_+}\\
	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_-}{1_-} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_-}{(d-1)_-}.
\end{align*}
The observables for $\LS(\Gamma_r)$ are
\begin{align}
	M_i = N_i = \Psi(x_i),
\end{align}
where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
Note that Alice uses the same observable for the same variable appearing in different equations.

To make sure the strategy is correct, we need to check a few properties of it.
\begin{proposition}
Let $M_1 = N_1 :=\Psi(a_1)$, $M_2 = N_2 := \Psi(a_2)$, $M_3 = N_3 := \Psi(a_3)$
and $M_4 = N_4 := \Psi(a_4)$, then
\begin{align}
	\label{eq:mn_preserve} &M_i N_i \ket{\psi} = \ket{\psi} && \text{for } i = 1 \dots 4,\\
	\label{eq:o2_comm} &(M_3M_4)M_2(M_4M_3) = M_2,
\end{align}
and similar commutation relation holds on Bob's side too.
\end{proposition}
\begin{proof}
	Since all the operators involved in this proposition act trivially on $W_2^{\x 2}$, we focus on
	their actions on $W_{d-1}$. In the later proof, by $\ket{\psi}$ we mean the part of $\ket{\psi}$ on $W_{d-1}$.

	We prove \cref{eq:o2_comm} first. It is simple to check that
	\begin{align*}
		&M_1M_2= \sum_{j=1}^{d-1} \omega_d^{j} \ketbra{x_j}{x_j},
		&&M_3M_4= \sum_{j=0}^{d-2} \ketbra{x_{r^{j-1}}}{x_{r^j}},
	\end{align*}
	and that 
	\begin{align*}
		M_3M_4 M_2 M_4 M_3 = &\sum_{j=0}^{(d-3)/2} M_3M_4 (\ketbra{x_{r^j}}{x_{r^{d-1-j}}}+\ketbra{x_{r^{d-1-j}}}{x_{r^j}}) M_4M_3\\
		=& \sum_{j=0}^{(d-3)/2} \ketbra{x_{r^{j-1}}}{x_{r^{d-2-j}}}+\ketbra{x_{r^{d-2-j}}}{x_{r^{j-1}}} = M_2.
	\end{align*}

	Next we prove \cref{eq:mn_preserve}. It is straightforward to see that $M_iN_i \ket{\psi} = \ket{\psi}$ for $i = 1,2$.
	Before checking $i=3$ and $i=4$, we first observe that
	\begin{align*}
		M_3M_4 N_3 N_4 \ket{\psi} = \ket{\psi}.
	\end{align*}
	The eigenvectors of $M_3M_4$ and $N_3N_4$ are 
        \begin{align*}
        		\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
        \end{align*}
        Hence we can express $\ket{x_{r^j}}$ in terms of $\ket{u_k}$ as 
        \begin{align*}
        		\ket{x_{r^j}} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
        \end{align*}
        Then $M_4$ acts on $\ket{x_{r^j}}$ by
        \begin{align*}
        		M_4 \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} M_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
        	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
        	=&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
        	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
        	=& \ket{x_{r^{d-1-j}}}.
        \end{align*}
        Then we show that $M_4  N_4 \ket{\psi} = \ket{\psi}$ as 
        \begin{align*}
        	M_4 N_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} M_4  N_4 \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} 
        	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}} =\ket{\psi},
        \end{align*}
	Combining it with the fact that $M_3M_4 N_3N_4 \ket{\psi} = \ket{\psi}$, we can conclude that
	$M_3N_3 \ket{\psi} = \ket{\psi}$.
\end{proof}
The similar result, i.e., $M_jN_j \ket{\psi} = \ket{\psi}$ for $j = 1 \dots \nr$, are easy to check because all the other observables are defined by $M_j, N_j$ for $j=1,2,3,4$.
An interesting property of $U_A := M_3M_4$ and $O_A := M_1M_2$ is summarized in the proposition below. 
\begin{lemma}
	\label{lm:uo_independ}
	The unitaries $O$ and $U$ of the form
	\begin{align}
		O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j} && U = \sum_{j=1}^{d-1}\ketbra{x_{j r^{-1}}}{x_j},
	\end{align}
	where $d$ is an odd prime number with primitive root $r$, generates
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
The proof of this lemma is provided in \cref{sec:u_and_o}.
Our self-test argument certifies that Alice and Bob has such $O$ and $U$ in their hands, so
it provides another angle to justify our self-testing argument.

%---------------------------------------------------
\subsection{The correlation $\fC(d,r)$}
%---------------------------------------------------
The full correlation is generated by the ideal strategy presented in the previous subsection.
To help readers understanding the proofs in \cref{sec:main} of this paper better, 
parts of the full correlation is given in the tables below.
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$x=\ast$}\\
\cline{3-4}
\multicolumn{2}{|c|}{} &$a = \diamond$ & $a = \perp$ \\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/(d-1) & 0 \\
\cline{2-4}
&$b=\perp$ & 0 & (d-3)/(d-1) \\
\hline
\end{tabular}
\caption{The correlation for $x=y=\ast$.}
\end{center}
\end{table}
